paper

### 2019-01-09 Report/paper.tex
push current status

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_7_0.png}\end{center}
        \caption{Distribution of papers published over the years}
        \label{fig1}
    \end{figure}

@@

\textbf{To glue back substrings} we exploit the fact that that APA
references all have the same initial structure: \emph{Lastname F.M.
(when published) Title which may contain colons and other non-alphabetic
chars. Where published. Who published} \cite{apaformat}. We thus check
that the beginning of each reference contains ``Lastname F.M. (when
published)''. It is relatively easy to check for this using regular
expressions as author names and year have a given structure. If a string
does not contain such a section, then it must be part of an other
reference, which is lies before in the list of reference substrings.
Note that this beginning is also what is added to the metadata as
identifying string. We found that in practical application it is
important to first merge lines if they were clearly cut off, as papers
with many authors may have the beginning on multiple lines. We can find
split up lines by checking for lines starting with non-alphabetic
characters or starting in a sentence. We merge these with the line
above. We can identify lines by their ending as being split up, such as
if they end in a comma, colon or only contain author names. We merge
these lines with the lines below them. Only then can we check whether a
line contains a valid citation start. If it does not we merge it with
the line above it. After this merging process we validate the returned
reference split by looking at the overall length and the initials, as
well as checking that a random sample returns satisfactory splitting
accuracy. We find that the above method of extracting the references
produces good results for proper APA citations and on APA citations
indeed outperforms Scolarcy when it comes to splitting up the lines.
\emph{To then get the subcomponents of a reference} is rather trivial,
as we can again use the structure of APA citations. The string before
the first parenthesis contains the authors names, inside the parentheses
we find the year or some other reference to publication time, after
which the title follows until the first dot. Then a reference to the
publishing venue follows.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_10_1.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figA}
    \end{figure}

@@

The header section itself contains information on the institution, but
as different was to list authors are accepted, notably two ways as can
be seen in \ref{figA} \ref{figB}. Hence, we first detect the structure
of the header section before extracting the association. We tag the
substring present in this section using a combination of \emph{named
entity detection}, using the implementation provided by \emph{spacy},
simple string comparison matching of the names of authors and
institutions we extracted from the metadata respectively from Approach 1
and tagging sections containing ``emails'' using regex , to detect where
in the header the email is. Then, taking the tagged section, we detect
which subsections correspond to which author-affiliation listing type,
and extract the author email - institution mapping accordingly.

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}9}]:} <IPython.core.display.HTML object>
\end{Verbatim}

@@

    \begin{Verbatim}[commandchars=\\\{\}]
Uploading 7403 kB. This may take a while{\ldots}

    \end{Verbatim}

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}11}]:} <IPython.core.display.HTML object>
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\}]
{\color{outcolor}Out[{\color{outcolor}13}]:} <IPython.core.display.HTML object>
\end{Verbatim}

@@

Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As graph is not connected, and contains one large main
component with 1141 authors and 208 very small components with less than
25 authors in them we focus on analyzing the structure of the main
component of the graph. First we aim to detect sub-communities within
the graph. Modularity is one measure used to find such communities. It
measures the connection strength within a community relative to the
strength of outgoing connections. Networks with high modularity have
dense connections between the nodes within modules but sparse
connections between nodes in different modules. A non-parametric
algorithm for community detection is the Louvain Method
\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
\cite{louvain}. This gives a good partitioning of the graph into 26
communities of median size 42.84. This is quite a large number of
communities, so we consider an alternative way to yield bigger
partitions. An alternate way to find subcommunities is to look at
normalized cuts, which partition the nodes into groups with many
within-group connections and relatively few between-group connections.
The advantage of this method is that we can choose how many cuts to
make, and we are thus able to define the size of subcommunities. Finding
normalized cuts in a graph can be done using \emph{sklearns} spectral
clustering algorithm by passing it the adjacency matrix of the graph.
With this method we are able to neatly separate the main component graph
in three large communities. We note that the clusters found using method
one are contained in the clusters found by method 2. See .

@@

@@

@@

@@

>>>>

@@

\textbf{To unify substrings} we exploit the fact that that APA
references all have the same initial structure: \emph{Lastname F.M.
(when published) Title which may contain colons and other non-alphabetic
chars. Where published. Who published} \cite{apaformat}. We thus check
that the beginning of each reference contains ``Lastname F.M. (when
published)''. It is relatively easy to check for this using regular
expressions as author names and year have a given structure. If a string
does not contain such a section, then it must be part of an other
reference, which is lies before in the list of reference substrings.
Note that this beginning is also what is added to the metadata as
identifying string. We found that in practical application it is
important to first merge lines if they were clearly cut off, as papers
with many authors may have the beginning on multiple lines. We can find
split up lines by checking for lines starting with non-alphabetic
characters or starting in a sentence. We merge these with the line
above. We can identify lines by their ending as being split up, such as
if they end in a comma, colon or only contain author names. We merge
these lines with the lines below them. Only then can we check whether a
line contains a valid citation start. If it does not we merge it with
the line above it. After this merging process we validate the returned
reference split by looking at the overall length and the initials, as
well as checking that a random sample returns satisfactory splitting
accuracy. We find that the above method of extracting the references
produces good results for proper APA citations and on APA citations
indeed outperforms Scolarcy when it comes to splitting up the lines.
\emph{To then get the subcomponents of a reference} is rather trivial,
as we can again use the structure of APA citations. The string before
the first parenthesis contains the authors names, inside the parentheses
we find the year or some other reference to publication time, after
which the title follows until the first dot. Then a reference to the
publishing venue follows.

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_11_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figB}
    \end{figure}

@@

The header section itself contains information on the institution, but
as different was to list authors are accepted, notably two ways as can
be seen in Figure \ref{figA} and Figure \ref{figB}. Hence, we first
detect the structure of the header section before extracting the
association. We tag the substring present in this section using a
combination of \emph{named entity detection}, using the implementation
provided by \emph{spacy}, simple string comparison matching of the names
of authors and institutions we extracted from the metadata respectively
from Approach 1 and tagging sections containing ``emails'' using regex ,
to detect where in the header the email is. Then, taking the tagged
section, we detect which subsections correspond to which
author-affiliation listing type, and extract the author email -
institution mapping accordingly.

@@

@@

@@

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
        \caption{One of the connected components of the co-authorship graph}
        \label{fig_plot}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_49_0.png}\end{center}
        \caption{Largest Component}
        \label{author_collab_large}
    \end{figure}

    Focusing in on the authors is not the only way to interpret the
co-authorship graph. One should also consider the overall structure of
the graph. As graph is not connected, and contains one large main
component with 1141 authors and 208 very small components with less than
25 authors in them we focus on analyzing the structure of the main
component of the graph. First we aim to detect sub-communities within
the graph. Modularity is one measure used to find such communities. It
measures the connection strength within a community relative to the
strength of outgoing connections. Networks with high modularity have
dense connections between the nodes within modules but sparse
connections between nodes in different modules. A non-parametric
algorithm for community detection is the Louvain Method
\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
\cite{louvain}. This gives a good partitioning of the graph into 26
communities of median size 42.84. This is quite a large number of
communities, so we consider an alternative way to yield bigger
partitions. An alternate way to find subcommunities is to look at
normalized cuts, which partition the nodes into groups with many
within-group connections and relatively few between-group connections.
The advantage of this method is that we can choose how many cuts to
make, and we are thus able to define the size of subcommunities. Finding
normalized cuts in a graph can be done using \emph{sklearns} spectral
clustering algorithm by passing it the adjacency matrix of the graph.
With this method we are able to neatly separate the main component graph
in three large communities. We note that the clusters found using method
one are contained in the clusters found by method 2. See Figure \ref{}
and Figure \ref{}.

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
        \caption{}
        \label{}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{unigraph}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
        \caption{Distribution of papers published over the years}
        \label{fig1}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
        \caption{Different formats used to reference institution}
        \label{figrep}
    \end{figure}

@@

    \begin{figure}
        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
        \caption{Collaborative papers between countries}
        \label{figcollab}
    \end{figure}
